Copulas and their potential for ecology: Appendices

### 2019-12-18 SupportingInformation.Rmd
continuing to trim words here and there

---
title: "Supporting information: Copulas and their potential for ecology"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance D. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
geometry: "left=1cm,right=1cm,top=2.2cm,bottom=2.2cm"

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=8 cm]{./Results/copula_pedagog_fig_BB1.pdf}
\caption[Lower- and upper-tail dependence can vary independently of correlation]{Lower- and 
upper-tail dependence can vary independently of correlation. (A-C) Data generated using the BB1 
copula (see section \ref{MT-Background} in the main text) 
with three different 
sets of parameters chosen to produce a variety of 
lower-tail (LT) and upper-tail (UT) dependence strengths, but with the same 
Kendall correlation (K) (to two digits) in all cases. (D-F) Similar to A-C, but
with stronger correlation. Asymmetry of tail dependence (LT-UT) is the same 
within each column. See section \ref{Background} in the main text for a formal description of 
tail dependence and other measures of association in the tails.\label{fig_cop_pedag}}
\end{center}
\end{figure}

>>>>

---
title: "Copulas and their potential for ecology: Appendices"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance D. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
geometry: "left=1cm,right=1cm,top=2.2cm,bottom=2.2cm"

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=8 cm]{./Results/copula_pedagog_fig_BB1.pdf}
\caption[Lower- and upper-tail dependence can vary independently of correlation]{Lower- and 
upper-tail dependence can vary independently of correlation. (A-C) Data generated using the BB1 
copula (see section \ref{MT-Background} in the main text) 
with three different 
sets of parameters chosen to produce a variety of 
lower-tail (LT) and upper-tail (UT) dependence strengths, but with the same 
Kendall correlation (K) (to two digits) in all cases. (D-F) Similar to A-C, but
with stronger correlation. Asymmetry of tail dependence (LT-UT) is the same 
within each column. See section \ref{MT-Background} in the main text for a formal description of 
tail dependence and other measures of association in the tails.\label{fig_cop_pedag}}
\end{center}
\end{figure}
